---
title: "Word Puzzle"
author: "R. Mark Sharp"
date: "4/14/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This RMarkdown document is a hidden word puzzle maker. The user provides a text file with one or
more words per line and the program tries to place those words into a matrix 
of characters that whose size is specified by the configuration specified at 
the end of the word file. The configuration section begins on the line after a
line beginning with a '#' symbol. An example file structure follows:

firstWord secondWord
thirdWord short verrryyyyyy loooonnnng wwwwwoooorrrrrd

#
max_trials = 10000
n_directions = 20
width = 17
height = 15
left_right = 0.3
right_left = 0.2
up_down = 0.2
down_up = 0.2
up_right = 0.1
up_left = 0.1
down_right = 0.1
down_left = 0.1

The numbers associated with the directions of word formation are 
used to determine the stochastic probability that the direction will 
be used for the word placement. 

A word placement may fail. Each word placement
attempts to place the word in the puzzle max_trials times before the placement
attempt is considered unsuccessful. 
he numbers associated with the directions of word formation are  also relative 
to each other and may be integers. Thus, a direction of formation that is
0.3 is going to be (on average) tried three times more often than a direction
that has a value of 0.1.
```{r}
library(wordPuzzle)
filename <- "inst/extdata/word_lists/books_of_bible.txt"
puzzle_list <- make_puzzle(filename, upper_case = TRUE)
```

```{r results='markup'}
print_puzzle(puzzle_list)
print_words(puzzle_list)
print_key(puzzle_list)

```
